---
title: "Reactable"
output:
  html_document:
    toc: true
    toc_float:
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(reactable)

options(reactable.static = TRUE)
```

## Basic Usage
To create a data table, use `reactable()` on a data frame or matrix.
The table will be sortable and paginated by default:
```{r}
library(reactable)

reactable(iris)
```

### Column definitions
Columns can be customized by providing a named list of column definitions
created by `colDef()` to `columns`:
```{r}
reactable(
  iris[1:5, ],
  columns = list(
    Sepal.Length = colDef(name = "Sepal Length"),
    Sepal.Width = colDef(name = "Sepal Width"),
    Species = colDef(align = "center")
  )
)
```

For convenience, you can also specify a default `colDef()` to use for all
columns in `defaultColDef`:
```{r}
reactable(
  iris[1:5, ],
  defaultColDef = colDef(
    header = function(value) gsub(".", " ", value, fixed = TRUE),
    cell = function(value) format(value, nsmall = 1),
    align = "center",
    minWidth = 70,
    headerStyle = list(background = "#f7f7f8")
  ),
  columns = list(
    Species = colDef(minWidth = 140)  # overrides the default
  ),
  bordered = TRUE,
  highlight = TRUE
)
```

## Sorting

Tables are sortable by default. You can sort a column by clicking on its
header, or sort multiple columns by holding the shift key while sorting.

Sorting toggles between ascending and descending order by default. To clear
the sort, hold the shift key while sorting, and the sorting will additionally
toggle between ascending, descending, and unsorted order.

::: {.callout-note}
**Note:** Ascending order means the lowest, first, or earliest values will appear first.
Descending order means the largest, last, or latest values will appear first.
:::

### Default sorted columns

You can set the default sorted columns by providing a vector of column names
to `defaultSorted`:

```{r}
reactable(iris[48:52, ], defaultSorted = c("Species", "Sepal.Length"))
```

You can also provide a named list to customize the default sort orders.
Use `"asc"` for ascending order, or `"desc"` for descending order:

```{r}
reactable(iris[48:52, ], defaultSorted = list(Species = "asc", Petal.Length = "desc"))
```

### Default sort order

Columns are sorted in ascending order first by default. To change the default sort
order for all columns in the table, set `defaultSortOrder` in `reactable()` to
`"asc"` for ascending order, or `"desc"` for descending order.

To change the sort order of an individual column, set `defaultSortOrder` in
its `colDef()` to `"asc"` or `"desc"`. The default sort order of the column takes
precedence over the table.

```{r}
reactable(
  iris[48:52, ],
  defaultSortOrder = "desc",
  columns = list(
    Species = colDef(defaultSortOrder = "asc")
  ),
  defaultSorted = c("Species", "Petal.Length")
)
```

### Sort missing values last

You can ignore missing values when sorting by setting `sortNALast` on a column:

```{r}
reactable(
  data.frame(
    n = c(1, 2, 3, -Inf, Inf),
    x = c(2, 3, 1, NA, NaN),
    y = c("aa", "cc", "bb", NA, NA)
  ),
  defaultColDef = colDef(sortNALast = TRUE),
  defaultSorted = "x"
)
```

### No sorting

You can disable sorting by setting `sortable` to `FALSE` on the table or column.
When only some columns are sortable, it can help to indicate sortable
columns using `showSortable`:

```{r}
reactable(
  iris[1:5, ],
  sortable = FALSE,
  showSortable = TRUE,
  columns = list(
    Petal.Width = colDef(sortable = TRUE),
    Petal.Length = colDef(sortable = TRUE)
  )
)
```

### Hide sort icons

You can hide sort icons by setting `showSortIcon` to `FALSE`. This is only
recommended when you want to use a [custom sort indicator](cookbook/cookbook.html#custom-sort-indicators).
```{r}
reactable(iris[1:5, ], showSortIcon = FALSE)
```


## Filtering

You can make columns filterable by setting `filterable = TRUE` in `reactable()`:

```{r}
data <- MASS::Cars93[1:20, c("Manufacturer", "Model", "Type", "AirBags", "Price")]

reactable(data, filterable = TRUE, minRows = 10)
```

To make specific columns filterable (or not), set `filterable` to `TRUE` or `FALSE` in `colDef()`:

```{r}
reactable(
  data,
  filterable = TRUE,
  columns = list(
    Price = colDef(filterable = FALSE)
  ),
  defaultPageSize = 5
)
```

### Custom filtering

Column filtering can be customized using the `filterMethod` and `filterInput` arguments
in `colDef()`. See the [Custom Filtering](custom-filtering.html) guide for more details
and examples.

This example shows basic usage of a custom filter method, changing filtering
on the `Manufacturer` column to be case-sensitive rather than case-insensitive.
(Try filtering for "bmw" and then "BMW").

```{r}
data <- MASS::Cars93[, c("Manufacturer", "Model", "Type", "Price")]

reactable(
  data,
  columns = list(
    Manufacturer = colDef(
      filterable = TRUE,
      # Filter by case-sensitive text match
      filterMethod = JS("function(rows, columnId, filterValue) {
        return rows.filter(function(row) {
          return row.values[columnId].indexOf(filterValue) !== -1
        })
      }")
    )
  ),
  defaultPageSize = 5
)
```

## Searching

You can make the entire table searchable by setting `searchable = TRUE` in `reactable()`:

```{r}
data <- MASS::Cars93[1:20, c("Manufacturer", "Model", "Type", "AirBags", "Price")]

reactable(data, searchable = TRUE, minRows = 10)
```

## Pagination

You can change the default page size by configuring `defaultPageSize`:

```{r}
reactable(iris[1:6, ], defaultPageSize = 4)
```

You can also set the minimum rows per page using `minRows`. This may be
useful when rows don't completely fill the page, or if the table has filtering:

```{r}
reactable(iris[1:6, ], defaultPageSize = 4, minRows = 4, searchable = TRUE)
```

### Page size options

You can show a dropdown of page sizes for users to choose from using `showPageSizeOptions`.
The page size options can be customized through `pageSizeOptions`:

```{r}
reactable(
  iris[1:12, ],
  showPageSizeOptions = TRUE,
  pageSizeOptions = c(4, 8, 12),
  defaultPageSize = 4
)
```

### Alternative pagination types

You can use an alternative pagination type by setting `paginationType` to:

- `"jump"` to show a page jump
- `"simple"` to show previous/next buttons only

#### Page jump

```{r}
reactable(iris[1:50, ], paginationType = "jump", defaultPageSize = 4)
```

#### Simple

```{r}
reactable(iris[1:50, ], paginationType = "simple", defaultPageSize = 4)
```

### Hide page info

You can hide page info by setting `showPageInfo` to `FALSE`:

```{r}
reactable(iris[1:12, ], showPageInfo = FALSE, defaultPageSize = 4)

reactable(iris[1:12, ], showPageInfo = FALSE, showPageSizeOptions = TRUE, defaultPageSize = 8)
```

### Always show pagination

By default, pagination is hidden if the table only has one page. To keep the
pagination shown, set `showPagination` to `TRUE`. This is especially useful if
you want to keep the page info showing the number of rows in the table.

```{r}
reactable(iris[1:5, ], showPagination = TRUE)
```

### No pagination

Tables are paginated by default, but you can disable pagination by setting `pagination` to `FALSE`:

```{r}
reactable(iris[1:20, ], pagination = FALSE, highlight = TRUE, height = 250)
```

::: {.callout-tip}
**Tip:** Disabling pagination is not recommended for large tables with many
interactive elements (such as links, expand buttons, or selection checkboxes),
as that can make it difficult for keyboard users to navigate the page.
:::

## Grouping and Aggregation

You can group rows in a table by specifying one or more columns in `groupBy`:

```{r}
data <- MASS::Cars93[10:22, c("Manufacturer", "Model", "Type", "Price", "MPG.city")]

reactable(data, groupBy = "Manufacturer")
```

When rows are grouped, you can aggregate data in a column using an `aggregate` function:

```{r}
data <- MASS::Cars93[14:38, c("Type", "Price", "MPG.city", "DriveTrain", "Man.trans.avail")]

reactable(
  data,
  groupBy = "Type",
  columns = list(
    Price = colDef(aggregate = "max"),
    MPG.city = colDef(aggregate = "mean", format = colFormat(digits = 1)),
    DriveTrain = colDef(aggregate = "unique"),
    Man.trans.avail = colDef(aggregate = "frequency")
  )
)
```

You can use one of the built-in aggregate functions:
```r
colDef(aggregate = "sum")        # Sum of numbers
colDef(aggregate = "mean")       # Mean of numbers
colDef(aggregate = "max")        # Maximum of numbers
colDef(aggregate = "min")        # Minimum of numbers
colDef(aggregate = "median")     # Median of numbers
colDef(aggregate = "count")      # Count of values
colDef(aggregate = "unique")     # Comma-separated list of unique values
colDef(aggregate = "frequency")  # Comma-separated counts of unique values
```

### Multiple groups
```{r}
data <- data.frame(
  State = state.name,
  Region = state.region,
  Division = state.division,
  Area = state.area
)

reactable(
  data,
  groupBy = c("Region", "Division"),
  columns = list(
    Division = colDef(aggregate = "unique"),
    Area = colDef(aggregate = "sum", format = colFormat(separators = TRUE))
  ),
  bordered = TRUE
)
```

### Include sub rows in pagination

By default, sub rows are excluded from pagination and always shown on the same
page when expanded. To include sub rows in pagination, you can set `paginateSubRows`
to `TRUE`. This is recommended for grouped tables with a large number of rows
where expanded rows may not all fit on one page.

```{r}
data <- MASS::Cars93[, c("Manufacturer", "Model", "Type", "Price", "MPG.city")]

reactable(data, groupBy = "Type", paginateSubRows = TRUE)
```


## Column Formatting

You can format data in a column by providing `colFormat()` options to the `format`
argument in `colDef()`.

The formatters for numbers, dates, times, and currencies are locale-sensitive and
automatically adapt to language preferences of the user's browser. This means, for
example, that users will see dates formatted in their own timezone or numbers formatted
in their own locale.

To use a specific locale for data formatting, provide a vector of BCP 47 language
tags in the `locales` argument. See a list of
[common BCP 47 language tags](https://learn.microsoft.com/en-us/openspecs/office_standards/ms-oe376/6c085406-a698-4e12-9d4d-c3b0ee3dbc4a)
for reference.

::: {.callout-note}
**Note:** Column formatters change how data is displayed without affecting the underlying
data. Sorting, filtering, and grouping will still work on the original data.
:::

```{r}
data <- data.frame(
  price_USD = c(123456.56, 132, 5650.12),
  price_INR = c(350, 23208.552, 1773156.4),
  number_FR = c(123456.56, 132, 5650.12),
  temp = c(22, NA, 31),
  percent = c(0.9525556, 0.5, 0.112),
  date = as.Date(c("2019-01-02", "2019-03-15", "2019-09-22"))
)

reactable(data, columns = list(
  price_USD = colDef(format = colFormat(prefix = "$", separators = TRUE, digits = 2)),
  price_INR = colDef(format = colFormat(currency = "INR", separators = TRUE, locales = "hi-IN")),
  number_FR = colDef(format = colFormat(locales = "fr-FR")),
  temp = colDef(format = colFormat(suffix = " °C")),
  percent = colDef(format = colFormat(percent = TRUE, digits = 1)),
  date = colDef(format = colFormat(date = TRUE, locales = "en-GB"))
))
```

### Date formatting

```{r}
datetimes <- as.POSIXct(c("2019-01-02 3:22:15", "2019-03-15 09:15:55", "2019-09-22 14:20:00"),
                        tz = "America/New_York")
data <- data.frame(
  datetime = datetimes,
  date = datetimes,
  time = datetimes,
  time_24h = datetimes,
  datetime_pt_BR = datetimes
)

reactable(data, columns = list(
  datetime = colDef(format = colFormat(datetime = TRUE)),
  date = colDef(format = colFormat(date = TRUE)),
  time = colDef(format = colFormat(time = TRUE)),
  time_24h = colDef(format = colFormat(time = TRUE, hour12 = FALSE)),
  datetime_pt_BR = colDef(format = colFormat(datetime = TRUE, locales = "pt-BR"))
))
```

### Currency formatting

```{r}
data <- data.frame(
  USD = c(12.12, 2141.213, 0.42, 1.55, 34414),
  EUR = c(10.68, 1884.27, 0.37, 1.36, 30284.32),
  INR = c(861.07, 152122.48, 29.84, 110, 2444942.63),
  JPY = c(1280, 226144, 44.36, 164, 3634634.61),
  MAD = c(115.78, 20453.94, 4.01, 15, 328739.73)
)

reactable(data, columns = list(
  USD = colDef(
    format = colFormat(currency = "USD", separators = TRUE, locales = "en-US")
  ),
  EUR = colDef(
    format = colFormat(currency = "EUR", separators = TRUE, locales = "de-DE")
  ),
  INR = colDef(
    format = colFormat(currency = "INR", separators = TRUE, locales = "hi-IN")
  ),
  JPY = colDef(
    format = colFormat(currency = "JPY", separators = TRUE, locales = "ja-JP")
  ),
  MAD = colDef(
    format = colFormat(currency = "MAD", separators = TRUE, locales = "ar-MA")
  )
))
```

### Formatting aggregated cells

Column formatters apply to both standard and aggregated cells by default. If you
want to format aggregated cells separately, provide a named list of `cell` and
`aggregated` options:

```{r, eval=FALSE}
colDef(
  format = list(
    cell = colFormat(...),       # Standard cells
    aggregated = colFormat(...)  # Aggregated cells
  )
)
```

For example, only the aggregated `States` are formatted here:

```{r}
data <- data.frame(
  States = state.name,
  Region = state.region,
  Area = state.area
)

reactable(
  data,
  groupBy = "Region",
  columns = list(
    States = colDef(
      aggregate = "count",
      format = list(
        aggregated = colFormat(suffix = " states")
      )
    ),
    Area = colDef(
      aggregate = "sum",
      format = colFormat(suffix = " mi²", separators = TRUE)
    )
  )
)
```

### Displaying missing values

Missing values are ignored by formatters and shown as empty cells by default.
You can customize their display text by setting `na` on a column:

```{r}
reactable(
  data.frame(
    n = c(1, 2, NA, 4, 5),
    x = c(55, 27, NA, NaN, 19),
    y = c(1, NA, 0.25, 0.55, NA)
  ),
  columns = list(
    x = colDef(na = "–", format = colFormat(prefix = "$")),
    y = colDef(na = "NA", format = colFormat(percent = TRUE))
  )
)
```



## Custom Rendering

You can customize how data is displayed using an R or JavaScript function
that returns custom content. R render functions support
[Shiny HTML tags](https://shiny.rstudio.com/articles/tag-glossary.html) (or
[`htmltools`](https://unleash-shiny.rinterface.com/htmltools-overview.html)) and
[HTML widgets](https://www.htmlwidgets.org/),
while JavaScript render functions allow for more dynamic behavior.

You can also render content as HTML using `colDef(html = TRUE)`. Note that all
raw HTML is escaped by default.



### Cell rendering

#### R render function

```{r}
data <- MASS::Cars93[1:5, c("Manufacturer", "Model", "Type", "AirBags", "Price")]

#https://en.wikipedia.org/wiki/List_of_Unicode_characters

reactable(data, columns = list(
  Model = colDef(cell = function(value, index) {
    # Render as a link
    url <- sprintf("https://wikipedia.org/wiki/%s_%s", data[index, "Manufacturer"], value)
    htmltools::tags$a(href = url, target = "_blank", as.character(value))
  }),
  AirBags = colDef(cell = function(value) {
    # Render as an X mark or check mark
    if (value == "None") "\u274c No" else "\u2714\ufe0f Yes"
  }),
  Price = colDef(cell = function(value) {
    # Render as currency
    paste0("$", format(value * 1000, big.mark = ","))
  })
))
```

#### JavaScript render function

```{r}
data <- MASS::Cars93[1:5, c("Manufacturer", "Model", "Type", "AirBags", "Price")]

reactable(data, columns = list(
  Model = colDef(html = TRUE, cell = JS('
    function(cellInfo) {
      // Render as a link
      const url = `https://wikipedia.org/wiki/${cellInfo.row["Manufacturer"]}_${cellInfo.value}`
      return `<a href="${url}" target="_blank">${cellInfo.value}</a>`
    }
  ')),
  AirBags = colDef(cell = JS("
    function(cellInfo) {
      // Render as an X mark or check mark
      return cellInfo.value === 'None' ? '\u274c No' : '\u2714\ufe0f Yes'
    }
  ")),
  Price = colDef(cell = JS("
    function(cellInfo) {
      // Render as currency
      return '$' + (cellInfo.value * 1000).toLocaleString()
    }
  "))
))
```

#### Embedding HTML widgets

```{r message=FALSE}
library(dplyr)
library(sparkline)

data <- chickwts %>%
  group_by(feed) %>%
  summarise(weight = list(weight)) %>%
  mutate(boxplot = NA, sparkline = NA)

reactable(data, columns = list(
  weight = colDef(cell = function(values) {
    sparkline(values, type = "bar", chartRangeMin = 0, chartRangeMax = max(chickwts$weight))
  }),
  boxplot = colDef(cell = function(value, index) {
    sparkline(data$weight[[index]], type = "box")
  }),
  sparkline = colDef(cell = function(value, index) {
    sparkline(data$weight[[index]])
  })
))
```

### Grouped cell rendering

```{r}
data <- MASS::Cars93[10:22, c("Manufacturer", "Model", "Type", "Price", "MPG.city")]

reactable(
  data,
  groupBy = c("Manufacturer", "Type"),
  columns = list(
    Manufacturer = colDef(
      # Render grouped cells without the row count
      grouped = JS("function(cellInfo) {
        return cellInfo.value
      }")
    ),
    Type = colDef(
      # Render grouped cells with the row count, only if there are multiple sub rows
      grouped = JS("function(cellInfo) {
        if (cellInfo.subRows.length > 1) {
          return cellInfo.value + ' (' + cellInfo.subRows.length + ')'
        }
        return cellInfo.value
      }")
    )
  )
)
```

### Aggregated cell rendering

```{r, message=FALSE}
library(dplyr)

set.seed(10)

data <- sample_n(tail(MASS::Cars93, 9), 30, replace = TRUE) %>%
  select(Manufacturer, Model, Type, Sales = Price)

reactable(
  data,
  groupBy = "Manufacturer",
  searchable = TRUE,
  columns = list(
    Model = colDef(aggregate = "unique"),
    Type = colDef(
      # Render aggregated value as a comma-separated list of unique values
      aggregated = JS("function(cellInfo) {
        const values = cellInfo.subRows.map(function(row) { return row['Type'] })
        const unique = values.reduce(function(obj, v) { obj[v] = true; return obj }, {})
        return Object.keys(unique).join(', ')
      }")
    ),
    Sales = colDef(
      aggregate = "sum",
      # Render aggregated cell as currency
      aggregated = JS("function(cellInfo) {
        return '$' + cellInfo.value.toFixed(2)
      }")
    )
  )
)
```

### Header rendering

::: {.callout}
This example requires reactable v0.3.0 or above.
:::

```{r}
library(htmltools)

reactable(
  iris[1:5, ],
  defaultColDef = colDef(header = function(value) {
    units <- div(style = "color: #737373", "cm")
    div(title = value, value, units)
  }),
  columns = list(
    Petal.Width = colDef(
      name = "Petal Width",
      html = TRUE,
      align = "left",
      header = JS('function(column) {
        return column.name + `<div style="color: #737373">cm</div>`
      }')
    ),
    Species = colDef(header = function(value) {
      tags$a(href = "https://wikipedia.org/wiki/List_of_Iris_species", value)
    })
  )
)
```


## Footers

You can add column footers using the `footer` argument in `colDef()`.

`footer` can either be custom content to render (e.g., a character string or HTML tag),
or a custom render function. 

### R render function {#footers-r-render-function}

```{r, message=FALSE}
library(dplyr)
library(htmltools)

data <- MASS::Cars93[18:47, ] %>%
  select(Manufacturer, Model, Type, Sales = Price)

reactable(
  data,
  defaultPageSize = 5,
  columns = list(
    Manufacturer = colDef(footer = "Total"),
    Sales = colDef(footer = function(values) sprintf("$%.2f", sum(values)))
  ),
  defaultColDef = colDef(footerStyle = list(fontWeight = "bold"))
)
```

### JavaScript render function {#footers-js-render-function}

::: {.callout}
This example requires reactable v0.3.0 or above.
:::

```{r}
reactable(
  data,
  searchable = TRUE,
  defaultPageSize = 5,
  minRows = 5,
  columns = list(
    Manufacturer = colDef(footer = "Total"),
    Sales = colDef(
      footer = JS("function(column, state) {
        let total = 0
        state.sortedData.forEach(function(row) {
          total += row[column.id]
        })
        return '$' + total.toFixed(2)
      }")
    )
  ),
  defaultColDef = colDef(footerStyle = list(fontWeight = "bold"))
)
```

### Embedding HTML widgets {#embedding-html-widgets-footers}

```{r}
library(sparkline)

reactable(
  iris[1:20, ],
  defaultPageSize = 5,
  bordered = TRUE,
  defaultColDef = colDef(footer = function(values) {
    if (!is.numeric(values)) return()
    sparkline(values, type = "box", width = 100, height = 30)
  })
)
```


## Conditional Styling

You can conditionally style a table using functions that return inline styles
or CSS classes. Just like with custom rendering, style functions can either be
in R or JavaScript.


### Cell styling

#### R style function

```{r}
reactable(sleep[1:6, ], columns = list(
  extra = colDef(
    style = function(value) {
      if (value > 0) {
        color <- "#008000"
      } else if (value < 0) {
        color <- "#e00000"
      } else {
        color <- "#777"
      }
      list(color = color, fontWeight = "bold")
    }
  )
))
```

#### JavaScript style function

::: {.callout}
This example requires reactable v0.3.0 or above.
:::

```{r}
reactable(sleep[1:6, ], columns = list(
  extra = colDef(
    style = JS("function(rowInfo) {
      const value = rowInfo.values['extra']
      let color
      if (value > 0) {
        color = '#008000'
      } else if (value < 0) {
        color = '#e00000'
      } else {
        color = '#777'
      }
      return { color: color, fontWeight: 'bold' }
    }")
  )
))
```

### Row styling

#### R style function

```{r row_styling, eval=FALSE}
reactable(sleep[1:6, ], 
  rowStyle = function(index) {
    if (sleep[index, "extra"] < -1) {
      list(background = "rgba(0, 0, 0, 0.05)")
    }
  }
)
```

```{css}
.bold {
  font-weight: bold;
}
```

```{r ref.label="row_styling", echo=FALSE}
```

#### JavaScript style function

::: {.callout}
This example requires reactable v0.3.0 or above.
:::

```{r}
reactable(sleep[1:6, ],
  rowStyle = JS("function(rowInfo) {
    if (rowInfo.values['extra'] < -1) {
      return { background: 'rgba(0, 0, 0, 0.05)' }
    }
  }")
)
```


## Table Styling

You can customize table styling using several options, which can all be combined:

### Highlight rows on hover

```{r}
reactable(iris[1:5, ], highlight = TRUE)
```

### Bordered

```{r}
reactable(iris[1:5, ], bordered = TRUE)
```

### Borderless

```{r}
reactable(iris[1:5, ], borderless = TRUE)
```

### Outlined

```{r}
reactable(iris[1:5, ], outlined = TRUE)
```

### Striped

```{r}
reactable(iris[1:5, ], striped = TRUE)
```

### Bordered + striped + highlighting

```{r}
reactable(iris[1:5, ], bordered = TRUE, striped = TRUE, highlight = TRUE)
```

### Outlined + borderless

```{r}
reactable(iris[1:5, ], outlined = TRUE, borderless = TRUE)
```

### Compact

```{r}
reactable(iris[1:5, ], compact = TRUE)
```

### No text wrapping

Long text is wrapped by default, but you can force text to fit on a single line
by setting `wrap` to `FALSE`:

```{r}
data <- aggregate(. ~ Species, iris, toString)

reactable(
  data,
  wrap = FALSE,
  resizable = TRUE,
  bordered = TRUE,
  columns = list(Petal.Length = colDef(name = "Petal Length (cm)", minWidth = 50))
)
```

### Fixed height + sticky header/footer

You can make tables scrollable by setting a fixed height or width.
Headers and footers are sticky by default, so they stay in place when scrolling.

Scrollable tables are automatically made focusable when navigating using a keyboard to
ensure that they're always accessible for keyboard users.

```{r}
reactable(
  iris[1:20, ],
  height = 270,
  striped = TRUE,
  defaultColDef = colDef(
    footer = function(values, name) {
      htmltools::div(name, style = list(fontWeight = 600))
    }
  )
)
```

### Column widths

By default, columns have a minimum width of 100px and stretch to fill the table.
You can control the width of a column using the following arguments in `colDef()`:

- `minWidth` - minimum width of the column in pixels (defaults to `100`)
- `maxWidth` - maximum width of the column in pixels
- `width` - fixed width of the column in pixels (overrides `minWidth` and `maxWidth`)

When columns stretch, `minWidth` also controls the ratio at which columns grow.
For example, if a table consists of 3 columns having `minWidth = 100` each,
the columns will stretch at a ratio of `100:100:100`. Each column will take up 1/3
of the table's width and not shrink below 100px.

Another example: if a table consists of three columns having minimum widths of
200px, 100px, and 100px, the columns will take up 50%, 25%, and 25% of the table's
width respectively:

```{r}
reactable(
  MASS::Cars93[1:6, c("Make", "Type", "Weight")],
  columns = list(
    Make = colDef(minWidth = 200),   # 50% width, 200px minimum
    Type = colDef(minWidth = 100),   # 25% width, 100px minimum
    Weight = colDef(minWidth = 100)  # 25% width, 100px minimum
  ),
  bordered = TRUE
)
```

### No full width

Tables are full width by default, but you can shrink the table to fit its
contents by setting `fullWidth` to `FALSE`:

```{r no_full_width_1, eval=FALSE}
reactable(
  MASS::Cars93[1:5, 1:5],
  fullWidth = FALSE,
  bordered = TRUE,
  defaultColDef = colDef(minWidth = 120)
)
```

<div style="overflow: auto;">
```{r ref.label="no_full_width_1", echo=FALSE}
```
</div>

You can also set a maximum or fixed width on the table:

```{r no_full_width_2, eval=FALSE}
reactable(
  MASS::Cars93[1:5, 1:5],
  bordered = TRUE,
  defaultColDef = colDef(minWidth = 120),
  # Set a maximum width on the table:
  style = list(maxWidth = 650),
  # Or a fixed width:
  width = 650
)
```

<div style="overflow: auto;">
```{r ref.label="no_full_width_2", echo=FALSE}
```
</div>

### Vertical alignment

You can change the vertical alignment of cell content using the `vAlign` or
`headerVAlign` arguments in `colDef()` and `colGroup()`. `vAlign` controls the
alignment of data cells, while `headerVAlign` controls the alignment of header cells.
Possible options are `"top"` (the default), `"center"`, and `"bottom"`.

```{r}
library(dplyr)
library(htmltools)

data <- starwars[1:6, ] %>%
  select(character = name, height, mass, gender, homeworld, species)

reactable(
  data,
  columns = list(
    character = colDef(
      name = "Character / Species",
      # Show species under character names
      cell = function(value, index) {
        species <- data$species[index]
        species <- if (!is.na(species)) species else "Unknown"
        div(
          div(style = list(fontWeight = 600), value),
          div(style = list(fontSize = "0.75rem"), species)
        )
      }
    ),
    species = colDef(show = FALSE)
  ),
  # Vertically center cells and bottom-align headers
  defaultColDef = colDef(vAlign = "center", headerVAlign = "bottom"),
  bordered = TRUE
)
```

### Custom CSS

For more control over styling, you can add custom class names to the table and
apply your own CSS:

```{r}
reactable(
  iris[1:18, ],
  defaultPageSize = 6,
  borderless = TRUE,
  class = "my-tbl",
  defaultColDef = colDef(headerClass = "my-header"),
  columns = list(
    Sepal.Width = colDef(class = "my-col"),
    Petal.Width = colDef(class = "my-col")
  ),
  rowClass = "my-row"
)
```

```{css, echo=FALSE}
.my-tbl {
  border: 1px solid rgba(0, 0, 0, 0.1);
}

.my-header {
  border-width: 1px;
}

.my-col {
  border-right: 1px solid rgba(0, 0, 0, 0.05);
}

.my-row:hover {
  background-color: #f5f8ff;
}
```

In R Markdown documents, you can embed CSS using a `css` language chunk:

```{r, echo=FALSE, comment=NA}
cat('```{css, echo=FALSE}
.my-tbl {
  border: 1px solid rgba(0, 0, 0, 0.1);
}

.my-header {
  border-width: 1px;
}

.my-col {
  border-right: 1px solid rgba(0, 0, 0, 0.05);
}

.my-row:hover {
  background-color: #f5f8ff;
}
```')
```

The examples here embed CSS for demonstration, but it's sometimes better to add CSS
through an external style sheet. To learn more about adding custom CSS through an
external style sheet:

- [Using custom CSS in R Markdown documents](https://bookdown.org/yihui/rmarkdown/html-document.html#custom-css)
- [Using custom CSS in Shiny apps](https://shiny.rstudio.com/articles/css.html)

::: {.callout-note}
**Note:** If you inspect a table's HTML, you might find CSS classes like `.rt-table` on
different elements of the table. These CSS classes are undocumented and subject to change,
so we recommend adding your own custom class names, or using [themes](#theming) to customize
parts of the table that aren't covered by the custom class names.
:::

## Theming

Themes provide a powerful way to customize table styling that can be reused
across tables. You can either set theme variables to change the default styles
(e.g., row stripe color), or add your own custom CSS to specific elements of the table.

To apply a theme, provide a `reactableTheme()` to `theme`:
```{r}
reactable(
  iris[1:30, ],
  searchable = TRUE,
  striped = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    cellPadding = "8px 12px",
    style = list(fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"),
    searchInputStyle = list(width = "100%")
  )
)
```

### Global theme

To set the default theme for all tables, use the global `reactable.theme` option:

```{r}
options(reactable.theme = reactableTheme(
  color = "hsl(233, 9%, 87%)",
  backgroundColor = "hsl(233, 9%, 19%)",
  borderColor = "hsl(233, 9%, 22%)",
  stripedColor = "hsl(233, 12%, 22%)",
  highlightColor = "hsl(233, 12%, 24%)",
  inputStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
  selectStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
  pageButtonHoverStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
  pageButtonActiveStyle = list(backgroundColor = "hsl(233, 9%, 28%)")
))

reactable(
  iris[1:30, ],
  filterable = TRUE,
  showPageSizeOptions = TRUE,
  striped = TRUE,
  highlight = TRUE,
  details = function(index) paste("Details for row", index)
)
```

```{r, echo=FALSE}
options(reactable.theme = NULL)
```

### Nested selectors

You can use nested CSS selectors in theme styles to target the current element,
using `&` as the selector, or other child elements (just like in Sass).
This is useful for adding pseudo-classes like `&:hover`, or adding styles in a
certain context like `.outer-container &`.

For example, to highlight headers when sorting:

```{r}
reactable(
  iris[1:5, ],
  columns = list(Sepal.Length = colDef(sortable = FALSE)),
  showSortable = TRUE,
  theme = reactableTheme(
    headerStyle = list(
      "&:hover[aria-sort]" = list(background = "hsl(0, 0%, 96%)"),
      "&[aria-sort='ascending'], &[aria-sort='descending']" = list(background = "hsl(0, 0%, 96%)"),
      borderColor = "#555"
    )
  )
)
```

Or to apply a dark theme when a parent element has a certain class, like `.dark`:

```{r theme_toggle, eval=FALSE}
theme <- reactableTheme(
  style = list(".dark &" = list(color = "#fff", background = "#282a36")),
  cellStyle = list(".dark &" = list(borderColor = "rgba(255, 255, 255, 0.15)")),
  headerStyle = list(".dark &" = list(borderColor = "rgba(255, 255, 255, 0.15)")),
  paginationStyle = list(".dark &" = list(borderColor = "rgba(255, 255, 255, 0.15)")),
  rowHighlightStyle = list(".dark &" = list(background = "rgba(255, 255, 255, 0.04)")),
  pageButtonHoverStyle = list(".dark &" = list(background = "rgba(255, 255, 255, 0.08)")),
  pageButtonActiveStyle = list(".dark &" = list(background = "rgba(255, 255, 255, 0.1)"))
)

tbl <- reactable(iris[1:12, ], highlight = TRUE, defaultPageSize = 6, theme = theme)

# Simple theme toggle button
tags$button(onclick = "document.querySelector('.themeable-tbl').classList.toggle('dark')",
            "Toggle light/dark")

# Start with the dark theme enabled
div(class = "themeable-tbl dark", tbl)
```

```{r ref.label="theme_toggle", echo=FALSE}
```

### Dynamic theming

Themes can also be functions that return a `reactableTheme()` for
context-specific styling.

For example, to style tables in RStudio R Notebooks only when a dark
editor theme is active:

```{r, eval=FALSE}
options(reactable.theme = function() {
  theme <- reactableTheme(
    color = "hsl(233, 9%, 85%)",
    backgroundColor = "hsl(233, 9%, 19%)",
    borderColor = "hsl(233, 9%, 22%)",
    stripedColor = "hsl(233, 12%, 22%)",
    highlightColor = "hsl(233, 12%, 24%)",
    inputStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
    selectStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
    pageButtonHoverStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
    pageButtonActiveStyle = list(backgroundColor = "hsl(233, 9%, 28%)")
  )

  if (isTRUE(getOption("rstudio.notebook.executing"))) {
    if (requireNamespace("rstudioapi", quietly = TRUE) && rstudioapi::getThemeInfo()$dark) {
      return(theme)
    }
  }
})
```


## Column Groups
You can create column groups by passing a list of `colGroup()` definitions to `columnGroups`:
```{r}
reactable(
  iris[1:5, ],
  columns = list(
    Sepal.Length = colDef(name = "Length"),
    Sepal.Width = colDef(name = "Width"),
    Petal.Length = colDef(name = "Length"),
    Petal.Width = colDef(name = "Width")
  ),
  columnGroups = list(
    colGroup(name = "Sepal", columns = c("Sepal.Length", "Sepal.Width")),
    colGroup(name = "Petal", columns = c("Petal.Length", "Petal.Width"))
  )
)
```


## Column Resizing
You can make columns resizable by setting `resizable` to `TRUE`:
```{r}
reactable(MASS::Cars93[1:5, ], resizable = TRUE, wrap = FALSE, bordered = TRUE)
```


## Sticky Columns

You can make columns sticky when scrolling horizontally using the `sticky`
argument in `colDef()` or `colGroup()`. Set `sticky` to either `"left"`
or `"right"` to make the column stick to the left or right side.

```{r}
reactable(
  MASS::Cars93[1:5, ],
  columns = list(
    Manufacturer = colDef(
      sticky = "left",
      # Add a right border style to visually distinguish the sticky column
      style = list(borderRight = "1px solid #eee"),
      headerStyle = list(borderRight = "1px solid #eee")
    ),
    Make = colDef(
      sticky = "right",
      # Add a left border style to visually distinguish the sticky column
      style = list(borderLeft = "1px solid #eee"),
      headerStyle = list(borderLeft = "1px solid #eee")
    )
  ),
  defaultColDef = colDef(minWidth = 150)
)
```

### Multiple sticky columns

```{r}
# Background style to visually distinguish sticky columns
sticky_style <- list(backgroundColor = "#f7f7f7")

reactable(
  MASS::Cars93[1:5, ],
  columns = list(
    Manufacturer = colDef(
      sticky = "left",
      style = sticky_style,
      headerStyle = sticky_style
    ),
    Model = colDef(
      sticky = "left",
      style = sticky_style,
      headerStyle = sticky_style
    ),
    Type = colDef(
      sticky = "left",
      style = sticky_style,
      headerStyle = sticky_style
    )
  ),
  resizable = TRUE,
  wrap = FALSE,
  bordered = TRUE
)
```

### Sticky column groups

If a column group is sticky, all columns in the group will automatically be
made sticky.

```{r}
reactable(
  MASS::Cars93[1:5, ],
  columnGroups = list(
    colGroup("Make", columns = c("Manufacturer", "Model"), sticky = "left"),
    colGroup("Price", columns = c("Min.Price", "Price", "Max.Price"), sticky = "left")
  ),
  defaultColDef = colDef(footer = "Footer"),
  resizable = TRUE,
  wrap = FALSE,
  bordered = TRUE
)
```


## Row Names and Row Headers

### Row names

Row names are shown by default if present. You can customize the row names column
using `".rownames"` as the column name:

```{r}
reactable(
  USPersonalExpenditure,
  columns = list(
    .rownames = colDef(name = "Category", sortable = TRUE)
  )
)
```

If row names haven't been set explicitly, you can force them to show by setting
`rownames` to `TRUE`:

```{r}
reactable(iris[1:5, ], rownames = TRUE)
```

### Row headers

You can mark up cells in a column as row headers by setting `rowHeader` to `TRUE`
in `colDef()`.

Use this to help users navigate the table using assistive technologies. When cells
are marked up as row headers, assistive technologies will read them aloud while
navigating through cells in the table.

Cells in the row names column are automatically marked up as row headers.

```{r}
data <- MASS::Cars93[1:5, c("Make", "Type", "Price", "MPG.city", "AirBags")]

reactable(
  data,
  columns = list(
    Make = colDef(rowHeader = TRUE, style = list(fontWeight = 600))
  ),
  bordered = TRUE
)
```


## Cell Click Actions
You can add cell click actions using the `onClick` argument, which accepts the
following values:

- `"expand"` to expand the row
- `"select"` to select the row
- A JavaScript function for a custom action, e.g., sending the click event to Shiny

### Expand on click
```{r}
reactable(
  iris[48:52, ],
  groupBy = "Species",
  details = function(index) paste("Details for row:", index),
  onClick = "expand",
  # Give rows a pointer cursor to indicate that they're clickable
  rowStyle = list(cursor = "pointer")
)
```

### Select on click
```{r}
reactable(iris[1:5, ], selection = "multiple", onClick = "select")
```

### Custom action

::: {.callout}
This example requires reactable v0.3.0 or above.
:::

This example uses a custom click action to create custom "show details" action
buttons in each row of the table:

```{r}
data <- cbind(
  MASS::Cars93[1:5, c("Manufacturer", "Model", "Type", "Price")],
  details = NA
)

reactable(
  data,
  columns = list(
    # Render a "show details" button in the last column of the table.
    # This button won't do anything by itself, but will trigger the custom
    # click action on the column.
    details = colDef(
      name = "",
      sortable = FALSE,
      cell = function() htmltools::tags$button("Show details")
    )
  ),
  onClick = JS("function(rowInfo, column) {
    // Only handle click events on the 'details' column
    if (column.id !== 'details') {
      return
    }

    // Display an alert dialog with details for the row
    window.alert('Details for row ' + rowInfo.index + ':\\n' + JSON.stringify(rowInfo.values, null, 2))

    // Send the click event to Shiny, which will be available in input$show_details
    // Note that the row index starts at 0 in JavaScript, so we add 1
    if (window.Shiny) {
      Shiny.setInputValue('show_details', { index: rowInfo.index + 1 }, { priority: 'event' })
    }
  }")
)
```

::: {.callout-warning}
**Warning:** Custom click actions are currently not accessible to keyboard
users, and are generally not recommended. If they must be used, ensure that
they can be triggered by a keyboard through other means, such as a button
in the example above.
:::

## Language Options

You can customize the language in the table by providing a set of `reactableLang()`
options to `language`:
```{r}
reactable(
  iris[1:30, ],
  searchable = TRUE,
  paginationType = "simple",
  language = reactableLang(
    searchPlaceholder = "Search...",
    noData = "No entries found",
    pageInfo = "{rowStart} to {rowEnd} of {rows} entries",
    pagePrevious = "\u276e",
    pageNext = "\u276f",

    # Accessible labels for assistive technologies such as screen readers.
    # These are already set by default, but don't forget to update them when
    # changing visible text.
    pagePreviousLabel = "Previous page",
    pageNextLabel = "Next page"
  )
)
```

### Global language options
To set the default language strings for all tables, use the global
`reactable.language` option:
```{r}
options(reactable.language = reactableLang(
  pageSizeOptions = "\u663e\u793a {rows}",
  pageInfo = "{rowStart} \u81f3 {rowEnd} \u9879\u7ed3\u679c,\u5171 {rows} \u9879",
  pagePrevious = "\u4e0a\u9875",
  pageNext = "\u4e0b\u9875"
))

reactable(iris[1:12, ], defaultPageSize = 4, showPageSizeOptions = TRUE)
```

```{r, echo=FALSE}
options(reactable.language = NULL)
```

## Shiny

To use reactable in Shiny apps, use `renderReactable()` and `reactableOutput()`:

```{r, eval=FALSE}
library(shiny)
library(reactable)

ui <- fluidPage(
  titlePanel("reactable example"),
  reactableOutput("table")
)

server <- function(input, output, session) {
  output$table <- renderReactable({
    reactable(iris)
  })
}

shinyApp(ui, server)
```

### Row selection

You can enable row selection by setting `selection` to `"single"`
for single selection, or `"multiple"` for multiple selection.

To get the selected rows in Shiny, use `getReactableState()`.
The selected rows are given as a vector of row indices
(e.g. `c(1, 6, 4)`) or `NULL` if no rows are selected.

```{r, eval=FALSE}
library(shiny)
library(reactable)

ui <- fluidPage(
  titlePanel("row selection example"),
  reactableOutput("table"),
  verbatimTextOutput("selected")
)

server <- function(input, output, session) {
  selected <- reactive(getReactableState("table", "selected"))

  output$table <- renderReactable({
    reactable(iris, selection = "multiple", onClick = "select")
  })

  output$selected <- renderPrint({
    print(selected())
  })

  observe({
    print(iris[selected(), ])
  })
}

shinyApp(ui, server)
```

#### Default selected rows

You can preselect rows by specifying a vector of row indices in `defaultSelected`:
```{r}
reactable(iris[1:4, ], selection = "multiple", defaultSelected = c(1, 3))
```


#### Customize the selection column

You can customize the selection column using `".selection"` as the column name:
```{r}
reactable(
  MASS::Cars93[1:4, ],
  columns = list(
    .selection = colDef(
      width = 80,
      sticky = "left",
      style = list(cursor = "pointer"),
      headerStyle = list(cursor = "pointer")
    )
  ),
  selection = "multiple",
  onClick = "select",
  resizable = TRUE,
  wrap = FALSE,
  bordered = TRUE
)
```

